---
title: "ACST886 Assignment2 Q3 5.8"
author: "Chang Liu"
date: "04/09/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE, message=FALSE)
```

## 5.8

### Processing data
```{r}
x<-c(30:49)
IExpose2risk<-c(70000,66672,68375,65420,61779,66091,68514,69560,65000,66279,67300,65368,65391,62917,66537,62302,62145,63856,61097,61110)
d_x<-c(39,43,34,31,23,50,48,43,48,47,62,63,84,86,120,121,122,162,151,184)
q_x<-d_x/IExpose2risk
```

### obtain function to estimate parameterusing weighted least squares
From the equation$ln(\frac{\dot{q_x}}{1-\dot{q_x}})=a+bx$
we can get $\dot{q_x}=\frac{e^{a+bx}}{1+e^{a+bx}}$
Thus we can find the parameters a and b by minimising:
$\sum_{x}w_x\left ( \hat{q_x}-\dot{q_x} \right )^2=\sum_{x}w_x\left ( \hat{q_x}-\frac{e^{a+bx}}{1+e^{a+bx}} \right )$

```{r}
f<-function(p){sum(IExpose2risk*(q_x-(exp(p[1]+p[2]*x)/(1+exp(p[1]+p[2]*x))))^2)}
```

### obtain initial values by regression
```{r}
junk<-glm(q_x~x,family = binomial(link=logit),weights = IExpose2risk)
iv<-as.numeric(junk$coefficients)
```

### using nlm function to get a,b using initial values.
```{r}
para<-nlm(f,iv)
a=para$estimate[1]
b=para$estimate[2]
a
b
```
### obtain graduate estimates using a and b
```{r}
q_grad<-exp(a+b*x)/(1+exp(a+b*x))
q_grad
```