---
title: "ACST886 Assignment2 Q2"
author: "Chang Liu"
date: "04/09/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data processing 

```{r}
Exposed2risk<-c(15518,19428,21594,21890,19174,15775,11414,6993,3276,1069,201)
deaths<-c(65,144,219,378,465,557,685,644,471,217,67)
Expec_death<-c(73.9,134.6,223.9,346.3,468.1,600.1,675.5,637.4,458.7,240.6,62.4)
```

## Claculate crude estimates and graduated estimates using binomial model 


```{r}
q_hat<-deaths/Exposed2risk
q_grad<-Expec_death/Exposed2risk
```

## Claculate standerised deviation
```{r}
z_x<-(deaths-Exposed2risk*q_grad)/sqrt(Exposed2risk*q_grad*(1-q_grad))
z_x
hist(z_x)
```
From the histgram of z_x we konw there are 3 of them fall in (-2,-1), 2 fall in (-1,0),5 fall in (0,1),1 fall in (1,2).
## Chi-square test

```{r}
test_stats1<-sum(z_x^2)
if(test_stats1>qchisq(0.95,length(z_x-1))){print("we reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is poor")}else{
  print("we do not reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is not poor")}
```

## Standerised deviations test
```{r}
A<-c(3,2,5,1)
E<-length(deaths)*c(0.16,0.34,0.34,0.16)
test_stats2<-sum((A-E)^2/E)
if(test_stats2>qchisq(0.95,length(z_x-1))){print("we reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is poor")}else{
  print("we do not reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is not poor")}
```
## Cumulative deviations test
```{r}
test_stats3<-sum(deaths-Exposed2risk*q_grad)/sqrt(sum(Exposed2risk*q_grad*(1-q_grad)))
if(test_stats3>1.96){print("we reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is poor")}else{
  print("we do not reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is not poor")}
```

## Sign test
From the histgram of z_x we konw there are 6 positive values.
```{r}
m<-length(deaths)
f<-function(a){choose(m,a)*0.5^m}
temp<-f(0)
for (i in 1:m) {
 if(temp<0.025){
   temp<-temp+f(i)
    }else{break("")}
  
}
k<-i
if(k<5){print("we reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is poor")}else{
  print("we do not reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is not poor")}

```

## Grouping of sign test
```{r}
n_1<-6
n_2<-5
g<-function(a){choose(n_1-1,a-1)*choose(n_2+1,a)/choose(n_1+n_2,n_1)}
temp<-g(1)
for (i in 2:m) {
 if(temp<0.05){
   temp<-temp+g(i)
    }else{break("")}
  
}
k<-i
if(k>6){print("we reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is poor")}else{
  print("we do not reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is not poor")}

```

Serial Correlations TEST
```{r}
z1_bar<-sum(z_x[1:10])/(m-1)
z2_bar<-sum(z_x[2:11])/(m-1)
test_stats4<-(sum((z_x[1:10]-z1_bar)*(z_x[2:11]-z2_bar))/sqrt(sum((z_x[1:10]-z1_bar)^2)*sum((z_x[2:11]-z2_bar)^2)))*sqrt(m-1)
if(test_stats4>1.64){print("we reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is poor")}else{
  print("we do not reject null hypothesis that at 5% significance level z_x is approximatly normal,thus the adherence to data is not poor")}
```
